---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# threedots

<!-- badges: start -->
![](https://img.shields.io/badge/language-R-blue)
![](https://img.shields.io/badge/status-experimental-yellow)
<!-- badges: end -->

Modify the dots (`...`) directly inside a function body.

## Installation

You can install the development version of threedots like so:

``` r
remotes::install_github("markheckmann/threedots")
```

## Example

The common way to modify the dots and pass them to another function is to use `do.call`:

```{r do-call}
fun <- \ (...) {
    dots <- list(...)
    dots$new_arg = 999
    do.call(list, dots)
}

fun(a = 1)
```

`{threedots}` allows to modify the dots directly via `modify_dots()`. It is basically just syntactic sugar for the `do.call` approach above.

```{r example}
library(threedots)

fun <- \ (...) {
    modify_dots(new_arg = 999)
    list(...)
}

fun(a = 1)
```

You may also use dots args inside `modify_dots()` for calculations using the `.()` function.

```{r}
fun <- \ (...) {
    modify_dots(a = .(a) * 100)
    list(...)
}

fun(a = 1)
```

There may be situations, where you need to clean the dots, so that they do not contain unknown arguments. Below, `fun()` does not know arg `c` and throws an error.

```{r clean-dots, error=T}
fun <- \(a = 1, b = 2) {
  list(a = a, b = b)  
}

foo <- \(...) {
  fun(...)
}

foo(c = -999)
```

One way to deal with that is again the `do.call` approach plus cleaning the list.

```{r}
foo <- \(...) {
  dots <- list(...)
  args_known <- names(formals(fun))
  args_given <- names(dots)
  args_keep <- intersect(args_given, args_known)
  do.call(fun, dots[args_keep])  # only insert known args
}
foo(a = 100, c = -999)
```
`safe_dots()` modifies the dots in place by removing all args unkown to `fun()`.

```{r}
foo <- \(...) {
  safe_dots(fun) # make dots safe to use with `fun`
  fun(...)
}

foo(a = 100, c = -999)
```
